User-level Grid Monitoring with Inca 2

### 2007-04-17 pubs/papers/hpdc-gmw-2007/paper.tex
split figure 5 into two figures since we have the space
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6856 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

%\begin{figure}[tbp]
%  \centering
%  \includegraphics[width=.8\columnwidth]{tg-deploy.eps}
%  \caption{\label{tg_deploy_fig} TeraGrid's Inca 2 Deployment.}
%\end{figure}
%\begin{figure}[tbp]
%  \centering
%  \includegraphics[width=.4\textwidth]{status-page.eps}
%  \caption{\label{status_page_fig} Portion of the TeraGrid CTSSv3 detailed status page with the resources anonymized.}
%\end{figure}

\begin{figure*}[tbp]
\subfigure[]{\includegraphics[width=.8\columnwidth]{tg-deploy.eps}}
\subfigure[]{\includegraphics[width=.6\textwidth]{status-page.eps}}
  \caption{\label{tg_deploy_fig}\label{status_page_fig} (a) TeraGrid's Inca 2
  deployment and (b) portion of the TeraGrid CTSSv3 detailed status page with
  the resources anonymized.}
\end{figure*}

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=.8\columnwidth]{tg-deploy.eps}
  \caption{\label{tg_deploy_fig} TeraGrid's Inca 2 Deployment.}
\end{figure}

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=.75\textwidth]{status-page.eps}
  \caption{\label{status_page_fig} Portion of the TeraGrid CTSSv3 detailed status page with the resources anonymized.}
\end{figure*}
